### 2019-03-07 manuscript/introduction.tex

%B: STOPPED HERE. 
Two methodological developments are critical for disentangling the relative importance of two or more traits in diversification.
First, \citet{fitzjohn_2012} extended the state-dependent diversification ``*SSE" modeling framework \citep{maddison2007}, to allow estimating the effect of an arbitrary number of states (enabling multiple states, MuSSE, instead of binary states, BiSSE).
This allows multiple states to represent trait combinations, particularly useful if one is interested in explicitly testing whether combinations of traits non-additively affect speciation or extinction.
Second, \citet{beaulieu_2016} proposed an extension of the state-dependent diversification ``*SSE" model framework \citep{maddison2007}, which allows modelling `hidden' or unspecified traits, linked to the trait of interest.
The presence of a hidden trait can uncover changes in the diversification rate due to unobserved sources of heterogeneity, not attributable to a focal trait.
These hidden-state  models have effectively shown that traits that were believed to be drivers of diversification, in reality are not, and that it is an unobserved but associated trait responsible for differences that are initially found. 
When the hidden state and not the focal trait, is responsible for changes in the diversification process, it leaves behind the question of whether the hidden state corresponds to a real state of a trait that should be sought, or whether it is an approximation of some unknowable heterogeneity, as well as whether interactions between the known and hidden trait were modeled appropriately.
Alternatively, one can simultaneously consider the effects of more than one known trait, especially in systems where multiple traits are suspected to influence diversification, and where interactions between those traits are well understood.

>>>>

%B: STOPPED HERE. 
Two methodological developments are critical for disentangling the relative importance of two or more traits in diversification.
First, \citet{fitzjohn_2012} extended the state-dependent diversification ``*SSE" modeling framework \citep{maddison_2007}, to allow estimating the effect of an arbitrary number of states (enabling multiple states, MuSSE, instead of binary states, BiSSE).
This allows multiple states to represent trait combinations, particularly useful if one is interested in explicitly testing whether combinations of traits non-additively affect speciation or extinction.
Second, \citet{beaulieu_2016} proposed an extension of the state-dependent diversification ``*SSE" model framework \citep{maddison_2007}, which allows modelling `hidden' or unspecified traits, linked to the trait of interest.
The presence of a hidden trait can uncover changes in the diversification rate due to unobserved sources of heterogeneity, not attributable to a focal trait.
These hidden-state  models have effectively shown that traits that were believed to be drivers of diversification, in reality are not, and that it is an unobserved but associated trait responsible for differences that are initially found. 
When the hidden state and not the focal trait, is responsible for changes in the diversification process, it leaves behind the question of whether the hidden state corresponds to a real state of a trait that should be sought, or whether it is an approximation of some unknowable heterogeneity, as well as whether interactions between the known and hidden trait were modeled appropriately.
Alternatively, one can simultaneously consider the effects of more than one known trait, especially in systems where multiple traits are suspected to influence diversification, and where interactions between those traits are well understood.
